---
title: "MuDyMust - Modelling"
author: "Küng, P., Höhener, P.S., Vieth, G., Spliesgart, A., Scholz, U., Rothman, A., Simpson, J."
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    theme: flatly
    df_print: kable
    toc: yes
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_folding: show
    toc_depth: 5
    highlight: tango
---


# Setup

```{r setup, message = FALSE, warning = FALSE, results = 'hide'}

library(tidyverse)
library(easystats)
library(cmdstanr)
library(knitr)
library(brms)
#install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
#cmdstanr::check_cmdstan_toolchain(fix = TRUE)
#cmdstanr::install_cmdstan()
library(remotes)
#remotes::install_github('Pascal-kueng/wbCorr')
library(wbCorr)
library(priorsense)
library(svglite)

source(file.path('Functions', 'PrettyTables.R'))
source(file.path('Functions', 'ReportModels.R'))
source(file.path('Functions', 'ReportMeasures.R'))
source(file.path('Functions', 'HurdleGaussianFamily.R'))

```


Setting general parameters
```{r}

system("shutdown /a") # prevent previously initialized shutdowns
shutdown = FALSE # restart after script finished or an error occurred (can be stoped within 180 seconds with command above)
check_models = FALSE 
get_bayesfactor = FALSE 

if (get_bayesfactor) {
  stats_to_report <- c('CI', 'SE', 'pd', 'ROPE', 'BF', 'Rhat', 'ESS')
} else {
  stats_to_report <- c('CI', 'SE', 'pd', 'ROPE', 'Rhat', 'ESS')
}

options(
  brms.backend = 'cmdstan',
  brms.file_refit = 'on_change',
  #brms.file_refit = 'always',
  error = function() {
    beepr::beep(sound = 5)
    if (shutdown) {
      system("shutdown /s /t 180")
      quit(save = "no", status = 1)
    }
  }
  , es.use_symbols = TRUE
)

set.seed(888)

```


Set model parameters
```{r}

iterations = 2000 # final models 12'000 per chain to achieve 40'000 needed for BF
warmup = 1000 # 2000 on final models

```


# Load merged dataset

```{r}

temp_script <- tempfile(fileext = ".R")
knitr::purl("01_harmonize_datasets.Rmd", output = temp_script)
source(temp_script)

head(df_merged) 

```

# Plot distributions of predictors

```{r}

hist(df_merged$emo_support)
hist(df_merged$pract_support)
hist(df_merged$pos_control)
hist(df_merged$neg_control)


```
# Plot MVPA

```{r}

hist(df_merged$mvpa, breaks=200)
plot(df_merged$day, df_merged$mvpa)
plot(df_merged$studyID, df_merged$mvpa)
plot(df_merged$dyad_type, df_merged$mvpa)

```


!todo: check for outliers, missing values (descriptive), and influential points

# Bivariate correlations

```{r}

cors <- wbCorr(
  df_merged, 
  cluster = 'id', 
  method = 'spearman'
)

summary(cors, 'wb')

```



# Modelling

## Positive Control

!todo: separate models for predictors that don't always co-occur

Create model and do prior predictive checks

```{r}

## Support
formula_control <- bf(
  mvpa ~ 
    (pos_control_cw + pos_control_cb + neg_control_cw + neg_control_cb) * dyad_type +
    (1 + pos_control_cw + neg_control_cw | studyID/id),
  family = negbinomial() # !todo: perhaps a hurdle lognormal model would be more appropriate
)


prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b"),
  brms::set_prior("normal(3.5, 2.5)", class = "Intercept", lb = 0),  # ~ 33 mins
  brms::set_prior("normal(0, 1.5)", class = "sd", lb = 0),
  brms::set_prior("normal(0.5, 1.5)", class = "shape", lb = 0)
)


## Fit the model using only the priors
m_control_prior <- brm(
  formula = formula_control, 
  data = df_merged, 
  prior = prior1,
  sample_prior = "only",  # draw from the priors only
  chains = 4, 
  iter = iterations, 
  warmup = warmup, 
  cores = 4, 
  backend = 'cmdstan',
  file = file.path('models', 'm_control_prior'),
  seed = 888
)

## Visualize the prior predictive distribution
pp_check(m_control_prior, type = 'hist')
summary(m_control_prior)

```


Estimating the model

```{r}

m_control <- brm(
  formula_control, 
  prior = prior1,
  data = df_merged, 
  chains = 4, 
  iter = iterations, 
  warmup = warmup, 
  cores = 4, 
  backend = 'cmdstan',
  file = file.path('models', 'm_control'),
  seed = 888
)

summary(m_control)

```


Assess Model Convergence and Fit

```{r}
if (check_models) {
  check_brms(m_control)
  DHARMa.check_brms.all(m_control)
}

```


Prior Sensitivity Checks

```{r}

if (check_models) {
  priorsense::powerscale_sensitivity(m_control)
  priorsense::powerscale_plot_dens(m_control)
  priorsense::powerscale_plot_ecdf(m_control)
  priorsense::powerscale_plot_quantities(m_control)
}

```


### Determining whether the slopes are significant for certain dyads

#### Within-Person 

```{r}

# Significance of slope for "Test" (reference category)
hypothesis(m_control, "pos_control_cw > 0")

# Significance of slope for "Romantic Partners"
hypothesis(m_control, "pos_control_cw + pos_control_cw:dyad_typeRomanticPartners> 0")

# Significance of slope for "Best Friends"
#hypothesis(m_control, "pos_control_cw + pos_control_cw:dyad_typeBestFriends> 0")

```

#### Between-Person
```{r}

# Significance of slope for "Test" (reference category)
hypothesis(m_control, "pos_control_cb > 0")

# Significance of slope for "Romantic Partners"
hypothesis(m_control, "pos_control_cb + pos_control_cb:dyad_typeRomanticPartners> 0")

# Significance of slope for "Best Friends"
#hypothesis(m_control, "pos_control_cw + pos_control_cw:dyad_typeBestFriends> 0")

```


# Plot effects and interactions

```{r}

eff <- conditional_effects(
  m_control,
  re_formula = NULL,
  #method = 'posterior_predict', # !todo: which one to use? epred, linpred or posterior predict?
  plot = FALSE
)

plot(eff, ask = FALSE)

```


## Pretty Interaction Plots (example)


```{r}

# Generate the conditional effects plot

cond_eff <- brms::conditional_effects(
  m_control, 
  effects = 'dyad_type:pos_control_cw'
)


plot_data <- cond_eff$`dyad_type:pos_control_cw`


my_colors <- c("#E69F00", "#009E73", "#56B4E9")

# Plot
ggplot(
  plot_data, 
  aes(
    x = pos_control_cw, 
    y = estimate__, 
    color = dyad_type, 
    fill = dyad_type,
    linetype = dyad_type
  )
) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.15) +
  geom_line(linewidth = 1.2) +
  labs(
    title = "Conditional Effects: Moderation",
    x = "Daily Positive Control",
    y = "Daily MVPA"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 10),
    legend.key.width = unit(2, 'cm'),
    legend.key.spacing.y = unit(0.2, 'cm'),
    legend.key.spacing = unit(0.5, 'cm'),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12),
    panel.grid.major = element_line(color = "lightgrey"),
    panel.grid.minor = element_blank()
  )

ggsave(
  file.path("Output", "Plot Interaction Color PSC.svg"),
  device = 'svg',
  width = 8,
  height = 5.6
  )


```



